---
title: "Cleaning up web scraped data"
author: "Mike Mahoney"
date: "February 24, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lubridate)
#library(varhandle)
library(tidyr)
```

```{r}
test <- read.csv("C:/Users/Mike/Crypto_Scraped_Data.csv")
ws_2017 <- read.csv("C:/Users/Mike/Crypto_Better_Scrape.csv", stringsAsFactors=FALSE)
ws_2017 <- ws_2017 %>% drop_na()
test_1 <- test
test_1 <- ws_2017
```

## This is changing Date into a "Date" >> Also converting our columns to numeric
```{r}
test_1$Date <- gsub("/", "" ,test_1$Date)
test_1$Date <- gsub(" ", "-", test_1$Date)
#test$Date <- as.Date(test$Date, format = "%y/%m/%d")
#test_1 <- test
#nzd$date <- format(as.Date(nzd$date, format = "%b-%d-%Y"), "%Y-%m-%d")
test_1$Date <- format(as.Date(test_1$Date, format = "%b-%d-%Y"), "%Y-%m-%d")
#test_1$Date <- mdy(test_1$Date)
crypto_ws <- test_1
test_1 <- NULL
test <- NULL
#crypto_ws <- format(crypto_ws, scientific = FALSE)
crypto_ws$Open <- as.numeric(crypto_ws$Open, options(digits=10))#options(nsmall=2)) #, scientific = FALSE)
crypto_ws$High <- as.numeric(crypto_ws$High) #, options(scipen = 999))
crypto_ws$Low <- as.numeric(crypto_ws$Low, options(digits=10))
crypto_ws$Close <- as.numeric(crypto_ws$Close, options(digits=10))
crypto_ws$Volume <- as.numeric(crypto_ws$Volume, options(digits=10))
crypto_ws$Market.Cap <- as.numeric(crypto_ws$Market.Cap, options(scipen = 999))
#class(crypto_ws$High)
#test_1$Date <- as.Date(test$Date, format = "%y/%m/%d")
```

## Adding our OHLC variable
```{r}
i = 1
for (i in 1:nrow(crypto_ws)) {
OHLC <- sum(crypto_ws[i,3:6]) #;OHLC
crypto_ws$OHLC[i] <- OHLC/4
}
```

## Adding Spread variable
```{r}
crypto_ws$Spread <- NULL
i = 1
for (i in 1:nrow(crypto_ws)) {
Spread <- (crypto_ws$High - crypto_ws$Low)
crypto_ws$Spread[i] <- Spread[i]
}
```

#Adding Days if the week so we can measure violitlity >> i.e: 4/28/13 is Sunday, Sunday has been added in the "day" column for data frame crytpo
```{r}
dow <- function(x) format(as.Date(x), "%A")
crypto_data_update <- dow(crypto_ws$Date)
crypto <- crypto_ws
crypto[["Day"]] <- crypto_data_update

```

#Creating a Bitcoin_ws subset >> To check if we are getting the same data from web scrape and Kaggle
```{r}
Bitcoin_ws <- subset(crypto, Slug == "bitcoin")

#Bitcoin[order(as.Date(Bitcoin$date, "%Y-%m-%d", decreasing = TRUE) ]
Bitcoin[order(as.Date(Bitcoin$date, "%Y-%m-%d"), decreasing = TRUE),]
#Bitcoin_1_year[order(as.Date(Bitcoin_1_year$date, "%Y-%m-%d"), decreasing = TRUE),]
BTC_1_yr_WS <- subset(Bitcoin_ws, Date >= "2017-01-01" & Date <= "2018-02-05")
date_range = seq(as.Date("2017-01-01"), as.Date("2018-02-05"), "days")

```

# This code takes the difference of the two datasets OHLC >> Which was 0!!!
```{r}
#seq(as.Date("1910/1/1"), as.Date("1999/1/1"), "years")

date_range = seq(as.Date("2017-01-01"), as.Date("2018-02-05"), "days")
#date_range = "2017-01-01" 
for (i in 1:401) {
  Bitcoin_1_year <- Bitcoin_1_year[order(as.Date(Bitcoin_1_year$date, "%Y-%m-%d"), decreasing = TRUE),]
  BTC_1_yr_WS <- BTC_1_yr_WS[order(as.Date(BTC_1_yr_WS$Date, "%Y-%m-%d"), decreasing = TRUE),]
  diff <- (BTC_1_yr_WS$OHLC - Bitcoin_1_year$OHLC)
  diff <- diff[i]
}
```


####### Creating the variables for Bitcoin_Ancient
## Loading the Ancient Bitcoin Data >> Applying thr similar formats >> to Bitcoin_Ancient
```{r}
Bitcoin_Ancient <- read.csv("C:/Users/Mike/Bitcoin_Scrape.csv")

Bitcoin_Ancient$Date <- gsub("/", "" ,Bitcoin_Ancient$Date)
Bitcoin_Ancient$Date <- gsub(" ", "-", Bitcoin_Ancient$Date)
Bitcoin_Ancient$Date <- format(as.Date(Bitcoin_Ancient$Date, format = "%b-%d-%Y"), "%Y-%m-%d")
#crypto_ws <- format(crypto_ws, scientific = FALSE)
Bitcoin_Ancient$Open <- as.numeric(Bitcoin_Ancient$Open, options(digits=10))#options(nsmall=2)) #, scientific = FALSE)
Bitcoin_Ancient$High <- as.numeric(Bitcoin_Ancient$High) #, options(scipen = 999))
Bitcoin_Ancient$Low <- as.numeric(Bitcoin_Ancient$Low, options(digits=10))
Bitcoin_Ancient$Close <- as.numeric(Bitcoin_Ancient$Close, options(digits=10))
Bitcoin_Ancient$Volume <- as.numeric(Bitcoin_Ancient$Volume, options(scipen = 999))
Bitcoin_Ancient$Market.Cap <- as.numeric(Bitcoin_Ancient$Market.Cap, options(scipen = 999))
```

## OHLC for Bitcoin_Ancient
```{r}
i = 1
for (i in 1:nrow(Bitcoin_Ancient)) {
OHLC <- sum(Bitcoin_Ancient[i,3:6]) #;OHLC
Bitcoin_Ancient$OHLC[i] <- OHLC/4
}
```

## Adding Spread variable for Bitcoin_Ancient
```{r}
#crypto_ws$Spread <- NULL
i = 1
for (i in 1:nrow(Bitcoin_Ancient)) {
Spread <- (Bitcoin_Ancient$High - Bitcoin_Ancient$Low)
Bitcoin_Ancient$Spread[i] <- Spread[i]
}
```

## Appending Our Data Sets >> Merging the Bitcoin subset with the scrape from 04/28/13 to 12/31/2016
```{r}
#Bitcoin_Ancient <- read.csv("C:/Users/Mike/Bitcoin_Scrape.csv")
Bitcoin <- subset(crypto_ws, Slug == "bitcoin")
Bitcoin_merge <- rbind(Bitcoin, Bitcoin_Ancient) 
Bitcoin <- Bitcoin_merge
Bitcoin_merge <- NULL
```

####### Creating the variables for Ripple_Ancient
## Loading the Ripple Ripple Data >> Applying thr similar formats >> to Ripple_Ancient
```{r}
Ripple_Ancient <- read.csv("C:/Users/Mike/Ripple_Scrape.csv")

Ripple_Ancient$Date <- gsub("/", "" ,Ripple_Ancient$Date)
Ripple_Ancient$Date <- gsub(" ", "-", Ripple_Ancient$Date)
Ripple_Ancient$Date <- format(as.Date(Ripple_Ancient$Date, format = "%b-%d-%Y"), "%Y-%m-%d")
#crypto_ws <- format(crypto_ws, scientific = FALSE)
Ripple_Ancient$Open <- as.numeric(Ripple_Ancient$Open, options(digits=10))#options(nsmall=2)) #, scientific = FALSE)
Ripple_Ancient$High <- as.numeric(Ripple_Ancient$High) #, options(scipen = 999))
Ripple_Ancient$Low <- as.numeric(Ripple_Ancient$Low, options(digits=10))
Ripple_Ancient$Close <- as.numeric(Ripple_Ancient$Close, options(digits=10))
Ripple_Ancient$Volume <- as.numeric(Ripple_Ancient$Volume, options(scipen = 999))
Ripple_Ancient$Market.Cap <- as.numeric(Ripple_Ancient$Market.Cap, options(scipen = 999))
```

## OHLC for Litecoin_Ancient
```{r}
i = 1
for (i in 1:nrow(Ripple_Ancient)) {
OHLC <- sum(Ripple_Ancient[i,3:6]) #;OHLC
Ripple_Ancient$OHLC[i] <- OHLC/4
}
```

## Adding Spread variable for Litecoin_Ancient
```{r}
#crypto_ws$Spread <- NULL
i = 1
for (i in 1:nrow(Ripple_Ancient)) {
Spread <- (Ripple_Ancient$High - Ripple_Ancient$Low)
Ripple_Ancient$Spread[i] <- Spread[i]
}
```

## Appending Our Data Sets >> Merging the Litecoin subset with the scrape from 01/01/2017 to 09/07/2017
```{r}
#Bitcoin_Ancient <- read.csv("C:/Users/Mike/Bitcoin_Scrape.csv")
Ripple <- subset(crypto_ws, Slug == "ripple")
Ripple_Merge <- rbind(Ripple, Ripple_Ancient) 
Ripple <- Ripple_Merge
Ripple_Merge <- NULL
```
