---
title: "Crypto Currency"
author: "Mike Mahoney"
date: "February 7, 2018"
output: html_document
---

## https://www.kaggle.com/jessevent/all-crypto-currencies >> Kaggle Link, where Data is obtained from

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("rugarch")  #This will install the Garch package
library(dplyr)
library(rugarch)
library(ggplot2)
```
Importing the data set
```{r}
crypto_data <- read.csv("C:/Users/Mike/Documents/Data Applications/all-crypto-currencies/crypto-markets.csv")
```

#Looking at our Data Set, getting a frequency of Symbol >> To see how many Cryptocurrencies are reported
Created a new Data Set >> crypto_data_1000 >> That includes the Cryptocurrencies with more than 1000 observatioons
```{r}
#crpto_data <- NULL
#summary(crpto_data)
count <- table(crypto_data$symbol)
crypto_data_1000 <- crypto_data[crypto_data$symbol %in% names(count)[count >=1000],]
```

#Adding Days if the week so we can measure violitlity >> i.e: 4/28/13 is Sunday, Sunday has been added in the "day" column for data frame crytpo
```{r}
dow <- function(x) format(as.Date(x), "%A")
crypto_data_update <- dow(crypto_data$date)
crypto <- crypto_data
crypto[["day"]] <- crypto_data_update

#Creating a "Day" for crypto_data_1000
dow <- function(x) format(as.Date(x), "%A")
crypto_data_update <- dow(crypto_data_1000$date)
crypto_data_1000[["day"]] <- crypto_data_update
```

#Getting an Average of Spread based on each day >>> NOTE: This gives the average spread by day
```{r}
Day_Spread_Avg <- tapply(Bitcoin$spread, Bitcoin$day, mean);Day_Spread_Avg
#tapply(df$ID , df$Emotion, mean) 
```

#### Slicig by Company
#Bitcoin >> Creating a Bitcoin slice of data to analyze this crytpocurrency
```{r}
Bitcoin <- subset(crypto_data_1000, symbol == "BTC")

```


#### Applying GARCH model to Bitcoin >> each chanhe in armaOrder is a chnage in how far back to use data
```{r}
Bitcoin_Garch_1 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(1,1)), distribution.model = "std")
Bitcoin_Garch_1_Results <- ugarchfit(spec = Bitcoin_Garch_1, data = Bitcoin$Close)

Bitcoin_Garch_2 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(2,2)), distribution.model = "std")
Bitcoin_Garch_2_Results <- ugarchfit(spec = Bitcoin_Garch_2, data = Bitcoin$Close);#Bitcoin_Garch_2_Results

Bitcoin_Garch_3 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(3,3)), distribution.model = "std")
Bitcoin_Garch_3_Results <- ugarchfit(spec = Bitcoin_Garch_3, data = Bitcoin$Close);#Bitcoin_Garch_3_Results

Bitcoin_Garch_4 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(9,9)), distribution.model = "std")
Bitcoin_Garch_4_Results <- ugarchfit(spec = Bitcoin_Garch_4, data = Bitcoin$Close);#Bitcoin_Garch_4_Results

#Bitcoin_Garch_5 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(15,15)), distribution.model = "std")
#Bitcoin_Garch_5_Results <- ugarchfit(spec = Bitcoin_Garch_5, data = Bitcoin$close);Bitcoin_Garch_5_Results
```

##Predicting Using GARCH
```{r}
label_list = c("24", "25", "26", "27", "28")
Bitcoin_Garch_Predict <- ugarchboot(Bitcoin_Garch_3_Results, n.ahead = 5, method = c("Partial", "Full")[1])
#plot(Bitcoin_Garch_Predict, which = 2, xlab = label_list, xlab = "Bitcoin Volatility")  #plot.window(xlim=c(low, high), ylim=c(high,low)))
#axis(1, at=1:5, labels = label_list)
plot(Bitcoin_Garch_Predict, which = 2) #, which = 2, type ="1", xlab = "Time")
```


This Model is currenlty forcasting 5 days >> From 02/05 to 02/10 >> Dark Blue Most Optimistic, Light Blue Pessemistic >> We know that Bitcoin closed at about $8550.00 

## Another GARCH Prediction
```{r}
Bitcoin_Garch_Predict_1 <- ugarchboot(Bitcoin_Garch_4_Results, n.ahead = 5, method = c("Partial", "Full")[1])
plot(Bitcoin_Garch_Predict_1, which = 2)
```
This Model is currenlty forcasting 5 days >> From 02/05 to 02/10 >> Dark Blue Most Optimistic, Light Blue Pessemistic >> We know that Bitcoin closed at about $8550.00 
>> Much Better using more days!


## Adding the OHLC >> Which is the Opening, High, Low, Close Average to the dataset >> Note: This is only to Bitcoin right now
```{r}
i = 1
for (i in 1:nrow(Bitcoin)) {
OHLC <- sum(Bitcoin[i,6:9]) #;OHLC
Bitcoin$OHLC[i] <- OHLC/4
}
```


## Plotting Bitcoin for 1 year
```{r}
Bitcoin$date <- as.Date(Bitcoin$date)
#df$date <- as.Date(df$date)
#Bitcoin_1_year <- Bitcoin[date >= "2018-02-05" & date <= "2017-02-05"]
Bitcoin_1_year <- subset(Bitcoin, date >= "2017-01-01" & date <= "2018-02-05")
Bitcoin_1_year <- Bitcoin_1_year[order(as.Date(Bitcoin_1_year$date, "%Y-%m-%d"), decreasing = TRUE),]
```

```{r}
#library(quantmod)
#FB <- getSymbols("FB", auto.assign = F)
#chartSeries(x= FB)

bc <- ggplot(data= Bitcoin_1_year, aes(x = date)) +
        geom_line(aes(y = Bitcoin$high, color = "red")) + 
        geom_line(aes(y = Bitcoin$OHLC, color = "black")) +
        geom_line(aes(y = Bitcoin$low, color = "green"))

bc


qplot(date,high, data=Bitcoin_1_year, geom="line")
qplot(date,Bitcoin_1_year$low, data=Bitcoin_1_year, geom="line")
```



####### The previous code was to test our model and get a template >>
  THe rest of the code will utilize the Web Scraped data "crypto_ws" 
  >> This code is formating our scraped data to our "fake, 2nd-ary source Kaggle"
  #### "crypto_ws" >> is our master scraped file denoted by "_ws"
```{r}
library(tidyr)
#test <- read.csv("C:/Users/Mike/Crypto_Scraped_Data.csv")
ws_2017 <- read.csv("C:/Users/Mike/Crypto_Better_Scrape.csv", stringsAsFactors=FALSE)
ws_2017 <- ws_2017 %>% drop_na()
#test_1 <- test
test_1 <- ws_2017
```

## This is changing Date into a "Date" >> Also converting our columns to numeric
```{r}
test_1$Date <- gsub("/", "" ,test_1$Date)
test_1$Date <- gsub(" ", "-", test_1$Date)
#test$Date <- as.Date(test$Date, format = "%y/%m/%d")
#test_1 <- test
#nzd$date <- format(as.Date(nzd$date, format = "%b-%d-%Y"), "%Y-%m-%d")
test_1$Date <- format(as.Date(test_1$Date, format = "%b-%d-%Y"), "%Y-%m-%d")
#test_1$Date <- mdy(test_1$Date)
crypto_ws <- test_1
test_1 <- NULL
test <- NULL
#crypto_ws <- format(crypto_ws, scientific = FALSE)
crypto_ws$Open <- as.numeric(crypto_ws$Open, options(digits=10))#options(nsmall=2)) #, scientific = FALSE)
crypto_ws$High <- as.numeric(crypto_ws$High) #, options(scipen = 999))
crypto_ws$Low <- as.numeric(crypto_ws$Low, options(digits=10))
crypto_ws$Close <- as.numeric(crypto_ws$Close, options(digits=10))
crypto_ws$Volume <- as.numeric(crypto_ws$Volume, options(digits=10))
crypto_ws$Market.Cap <- as.numeric(crypto_ws$Market.Cap, options(scipen = 999))
#class(crypto_ws$High)
#test_1$Date <- as.Date(test$Date, format = "%y/%m/%d")
```

## Adding our OHLC variable
```{r}
i = 1
for (i in 1:nrow(crypto_ws)) {
OHLC <- sum(crypto_ws[i,3:6]) #;OHLC
crypto_ws$OHLC[i] <- OHLC/4
}
```

## Adding Spread variable
```{r}
crypto_ws$Spread <- NULL
i = 1
for (i in 1:nrow(crypto_ws)) {
Spread <- (crypto_ws$High - crypto_ws$Low)
crypto_ws$Spread[i] <- Spread[i]
}
```

#Adding Days if the week so we can measure violitlity >> i.e: 4/28/13 is Sunday, Sunday has been added in the "day" column for data frame crytpo
```{r}
dow <- function(x) format(as.Date(x), "%A")
crypto_data_update <- dow(crypto_ws$Date)
crypto <- crypto_ws
crypto[["Day"]] <- crypto_data_update

```

#### Now that we have "crypto_ws" >> Properly formatted lets get to business

#####Dogecoin >> Such a cute puppy
# Creating a Subset for each cryptocurrency we want to evaluate >> #cryp_list = ["bitcoin", "dogecoin", "ethereum", "ripple", "litecoin", "neo", "maker", "tether"]
## Note: "ripple" was not completely scrapped due to... "server issues" >> Working on it!
#    & Maker is a newer currecny
```{r}
Bitcoin <- subset(crypto_ws, Slug == "bitcoin")
Dogecoin <- subset(crypto_ws, Slug == "dogecoin")
Ethereum <-  subset(crypto_ws, Slug == "ethereum")
Ripple <-  subset(crypto_ws, Slug == "ripple")
Litecoin <-  subset(crypto_ws, Slug == "litecoin")
Neo <-  subset(crypto_ws, Slug == "neo")
Maker <-  subset(crypto_ws, Slug == "maker")
Tether <-  subset(crypto_ws, Slug == "tether")
```
########### Ok Inverting our dataset >> I was an ID10T, This is a problem solver! >> Everything should work now!!!!

```{r}
Bitcoin <- Bitcoin[rev(rownames(Bitcoin)),]
Dogecoin <- Dogecoin[rev(rownames(Dogecoin)),]
Ethereum <- Ethereum[rev(rownames(Ethereum)),]
Ripple <- Ripple[rev(rownames(Ripple)),]
Litecoin <- Litecoin[rev(rownames(Litecoin)),]
Neo <- Neo[rev(rownames(Neo)),]
Maker <- Maker[rev(rownames(Maker)),]
Tether <- Tether[rev(rownames(Tether)),]
```


####### Creating the variables for Bitcoin_Ancient
## Loading the Ancient Bitcoin Data >> Applying thr similar formats >> to Bitcoin_Ancient
```{r}
Bitcoin_Ancient <- read.csv("C:/Users/Mike/Bitcoin_Scrape.csv")

Bitcoin_Ancient$Date <- gsub("/", "" ,Bitcoin_Ancient$Date)
Bitcoin_Ancient$Date <- gsub(" ", "-", Bitcoin_Ancient$Date)
Bitcoin_Ancient$Date <- format(as.Date(Bitcoin_Ancient$Date, format = "%b-%d-%Y"), "%Y-%m-%d")
#crypto_ws <- format(crypto_ws, scientific = FALSE)
Bitcoin_Ancient$Open <- as.numeric(Bitcoin_Ancient$Open, options(digits=10))#options(nsmall=2)) #, scientific = FALSE)
Bitcoin_Ancient$High <- as.numeric(Bitcoin_Ancient$High) #, options(scipen = 999))
Bitcoin_Ancient$Low <- as.numeric(Bitcoin_Ancient$Low, options(digits=10))
Bitcoin_Ancient$Close <- as.numeric(Bitcoin_Ancient$Close, options(digits=10))
Bitcoin_Ancient$Volume <- as.numeric(Bitcoin_Ancient$Volume, options(scipen = 999))
Bitcoin_Ancient$Market.Cap <- as.numeric(Bitcoin_Ancient$Market.Cap, options(scipen = 999))


## OHLC for Bitcoin_Ancient

i = 1
for (i in 1:nrow(Bitcoin_Ancient)) {
OHLC <- sum(Bitcoin_Ancient[i,3:6]) #;OHLC
Bitcoin_Ancient$OHLC[i] <- OHLC/4
}


## Adding Spread variable for Bitcoin_Ancient

#crypto_ws$Spread <- NULL
i = 1
for (i in 1:nrow(Bitcoin_Ancient)) {
Spread <- (Bitcoin_Ancient$High - Bitcoin_Ancient$Low)
Bitcoin_Ancient$Spread[i] <- Spread[i]
}


## Appending Our Data Sets >> Merging the Bitcoin subset with the scrape from 04/28/13 to 12/31/2016

#Bitcoin_Ancient <- read.csv("C:/Users/Mike/Bitcoin_Scrape.csv")
Bitcoin <- subset(crypto_ws, Slug == "bitcoin")
Bitcoin_merge <- rbind(Bitcoin, Bitcoin_Ancient)
Bitcoin <- Bitcoin_merge
#Bitcoin$OHLC <- round(Bitcoin$OHLC, digits = -2)
Bitcoin_merge <- NULL
```

####### Creating the variables for Ripple_Ancient
## Loading the Ripple Bitcoin Data >> Applying thr similar formats >> to Ripple_Ancient
```{r}
Ripple_Ancient <- read.csv("C:/Users/Mike/Ripple_Scrape.csv")

Ripple_Ancient$Date <- gsub("/", "" ,Ripple_Ancient$Date)
Ripple_Ancient$Date <- gsub(" ", "-", Ripple_Ancient$Date)
Ripple_Ancient$Date <- format(as.Date(Ripple_Ancient$Date, format = "%b-%d-%Y"), "%Y-%m-%d")
#crypto_ws <- format(crypto_ws, scientific = FALSE)
Ripple_Ancient$Open <- as.numeric(Ripple_Ancient$Open, options(digits=10))#options(nsmall=2)) #, scientific = FALSE)
Ripple_Ancient$High <- as.numeric(Ripple_Ancient$High) #, options(scipen = 999))
Ripple_Ancient$Low <- as.numeric(Ripple_Ancient$Low, options(digits=10))
Ripple_Ancient$Close <- as.numeric(Ripple_Ancient$Close, options(digits=10))
Ripple_Ancient$Volume <- as.numeric(Ripple_Ancient$Volume, options(scipen = 999))
Ripple_Ancient$Market.Cap <- as.numeric(Ripple_Ancient$Market.Cap, options(scipen = 999))


## OHLC for Litecoin_Ancient

i = 1
for (i in 1:nrow(Ripple_Ancient)) {
OHLC <- sum(Ripple_Ancient[i,3:6]) #;OHLC
Ripple_Ancient$OHLC[i] <- OHLC/4
}


## Adding Spread variable for Litecoin_Ancient

#crypto_ws$Spread <- NULL
i = 1
for (i in 1:nrow(Ripple_Ancient)) {
Spread <- (Ripple_Ancient$High - Ripple_Ancient$Low)
Ripple_Ancient$Spread[i] <- Spread[i]
}


## Appending Our Data Sets >> Merging the Litecoin subset with the scrape from 01/01/2017 to 09/07/2017

#Bitcoin_Ancient <- read.csv("C:/Users/Mike/Bitcoin_Scrape.csv")
Ripple <- subset(crypto_ws, Slug == "ripple")
Ripple_Merge <- rbind(Ripple, Ripple_Ancient) 
Ripple <- Ripple_Merge
Ripple_Merge <- NULL
```

#####Dogecoin >> Such a cute puppy
## Dogecoin GARCH model building! >> We are using the OHLC variable this time >>
```{r}
Dogecoin_Garch_1 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(1,1)), distribution.model = "std")
Dogecoin_Garch_1_Results <- ugarchfit(spec = Dogecoin_Garch_1, data = Dogecoin$Close)

Dogecoin_Garch_2 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(2,2)), distribution.model = "std")
Dogecoin_Garch_2_Results <- ugarchfit(spec = Dogecoin_Garch_2, data = Dogecoin$Close)#;Dogecoin_Garch_2_Results

Dogecoin_Garch_3 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(3,3)), distribution.model = "std")
Dogecoin_Garch_3_Results <- ugarchfit(spec = Dogecoin_Garch_3, data = Dogecoin$Close)#;Dogecoin_Garch_3_Results

Dogecoin_Garch_4 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(9,9)), distribution.model = "std")
Dogecoin_Garch_4_Results <- ugarchfit(spec = Dogecoin_Garch_4, data = Dogecoin$Close)#;Dogecoin_Garch_4_Results
```

## Predicting Dogecoin 5 days out >> Using 3 days
```{r}
#Dogecoin_Garch_Predict <- ugarchforecast(Dogecoin_Garch_3_Results, n.ahead = 5)

Dogecoin_Garch_Predict <- ugarchboot(Dogecoin_Garch_3_Results, n.ahead = 5, method = c("Partial", "Full")[1])
plot(Dogecoin_Garch_Predict, which = 2)
```
## Predicting Dogecoin 5 days out >> Using 9 days
```{r}
Dogecoin_Garch_Predict_1 <- ugarchboot(Dogecoin_Garch_4_Results, n.ahead = 5, method = c("Partial", "Full")[1])
plot(Dogecoin_Garch_Predict_1, which = 2)
```

## Ethereum GARCH model building! >> We are using the Close variable this time >>
```{r}
Ethereum_Garch_1 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(1,1)), distribution.model = "std")
Ethereum_Garch_1_Results <- ugarchfit(spec = Ethereum_Garch_1, data = Ethereum$Close)

Ethereum_Garch_2 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(2,2)), distribution.model = "std")
Ethereum_Garch_2_Results <- ugarchfit(spec = Ethereum_Garch_2, data = Ethereum$Close)#;Ethereum_Garch_2_Results

Ethereum_Garch_3 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(3,3)), distribution.model = "std")
Ethereum_Garch_3_Results <- ugarchfit(spec = Ethereum_Garch_3, data = Ethereum$Close)#;Ethereum_Garch_3_Results

Ethereum_Garch_4 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(7,7)), distribution.model = "std")
Ethereum_Garch_4_Results <- ugarchfit(spec = Ethereum_Garch_4, data = Ethereum$Close)#;Ethereum_Garch_4_Results
```

## Predicting Ethereum 5 days out >> Using 3 days
```{r}
Ethereum_Garch_Predict <- ugarchboot(Ethereum_Garch_3_Results, n.ahead = 5, method = c("Partial", "Full")[1])
plot(Ethereum_Garch_Predict, which = 2)
```

# Predicting Ethereum 5 days out >> Using 7 days
```{r}
Ethereum_Garch_Predict_1 <- ugarchboot(Ethereum_Garch_4_Results, n.ahead = 5, method = c("Partial", "Full")[1])
plot(Ethereum_Garch_Predict_1, which = 2)
```

## Ripple GARCH model building! >> We are using the Close variable this time >>
```{r}
Ripple_Garch_1 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(1,1)), distribution.model = "std")
Ripple_Garch_1_Results <- ugarchfit(spec = Ripple_Garch_1, data = Ripple$Close)

Ripple_Garch_2 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(2,2)), distribution.model = "std")
Ripple_Garch_2_Results <- ugarchfit(spec = Ripple_Garch_2, data = Ripple$Close)#;Ripple_Garch_2_Results

Ripple_Garch_3 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(3,3)), distribution.model = "std")
Ripple_Garch_3_Results <- ugarchfit(spec = Ripple_Garch_3, data = Ripple$Close)#;Ripple_Garch_3_Results

Ripple_Garch_4 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(7,7)), distribution.model = "std")
Ripple_Garch_4_Results <- ugarchfit(spec = Ripple_Garch_4, data = Ripple$Close)#;Ripple_Garch_4_Results
```

## Predicting Ripple 5 days out >> Using 3 days
```{r}
Ripple_Garch_Predict <- ugarchboot(Ripple_Garch_3_Results, n.ahead = 5, method = c("Partial", "Full")[1])
plot(Ripple_Garch_Predict, which = 2)
```
## Predicting Ripple 5 days out >> Using 7 days
```{r}
Ripple_Garch_Predict_1 <- ugarchboot(Ripple_Garch_4_Results, n.ahead = 5, method = c("Partial", "Full")[1])
plot(Ripple_Garch_Predict_1, which = 2)
```

## Litecoin GARCH model building! >> We are using the Close variable this time >>
```{r}
Litecoin_Garch_1 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(1,1)), distribution.model = "std")
Litecoin_Garch_1_Results <- ugarchfit(spec = Litecoin_Garch_1, data = Litecoin$Close)

Litecoin_Garch_2 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(2,2)), distribution.model = "std")
Litecoin_Garch_2_Results <- ugarchfit(spec = Litecoin_Garch_2, data = Litecoin$Close)#;Litecoin_Garch_2_Results

Litecoin_Garch_3 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(3,3)), distribution.model = "std")
Litecoin_Garch_3_Results <- ugarchfit(spec = Litecoin_Garch_3, data = Litecoin$Close)#;Ripple_Garch_3_Results

Litecoin_Garch_4 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(8,8)), distribution.model = "std")
Litecoin_Garch_4_Results <- ugarchfit(spec = Litecoin_Garch_4, data = Litecoin$Close)#;Ripple_Garch_4_Results
```

## Predicting Litecoin 5 days out >> Using 3 days
```{r}
Litecoin_Garch_Predict <- ugarchboot(Litecoin_Garch_3_Results, n.ahead = 5, method = c("Partial", "Full")[1])
plot(Litecoin_Garch_Predict, which = 2)
```
## Predicting Litecoin 5 days out >> Using 8 days >> Dark Blue Most Optimistic, Light Blue Pessemistic
```{r}
Litecoin_Garch_Predict_1 <- ugarchboot(Litecoin_Garch_4_Results, n.ahead = 5, method = c("Partial", "Full")[1])
plot(Litecoin_Garch_Predict_1, which = 2)
```

## Neo GARCH model building! >> We are using the Close variable this time >>
```{r}
Neo_Garch_1 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(1,1)), distribution.model = "std")
Neo_Garch_1_Results <- ugarchfit(spec = Neo_Garch_1, data = Neo$Close)

Neo_Garch_2 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(2,2)), distribution.model = "std")
Neo_Garch_2_Results <- ugarchfit(spec = Neo_Garch_2, data = Neo$Close)#;Neo_Garch_2_Results

Neo_Garch_3 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(3,3)), distribution.model = "std")
Neo_Garch_3_Results <- ugarchfit(spec = Neo_Garch_3, data = Neo$Close)#;Neo_Garch_3_Results

Neo_Garch_4 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(8,8)), distribution.model = "std")
Neo_Garch_4_Results <- ugarchfit(spec = Neo_Garch_4, data = Neo$Close)#;Neo_Garch_4_Results
```

## Predicting Litecoin 5 days out >> Using 3 days
```{r}
Neo_Garch_Predict <- ugarchboot(Neo_Garch_3_Results, n.ahead = 5, method = c("Partial", "Full")[1])
plot(Neo_Garch_Predict, which = 2)
```
## Predicting Litecoin 5 days out >> Using 8 days
```{r}
Neo_Garch_Predict_1 <- ugarchboot(Neo_Garch_4_Results, n.ahead = 5, method = c("Partial", "Full")[1])
plot(Neo_Garch_Predict_1, which = 2)
```

## Maker GARCH model building! >> We are using the Close variable this time >>
```{r}
Maker_Garch_1 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(1,1)), distribution.model = "std")
Maker_Garch_1_Results <- ugarchfit(spec = Maker_Garch_1, data = Maker$Close)

Maker_Garch_2 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(2,2)), distribution.model = "std")
Maker_Garch_2_Results <- ugarchfit(spec = Maker_Garch_2, data = Maker$Close)#;Maker_Garch_2_Results

Maker_Garch_3 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(3,3)), distribution.model = "std")
Maker_Garch_3_Results <- ugarchfit(spec = Maker_Garch_3, data = Maker$Close)#;Maker_Garch_3_Results

Maker_Garch_4 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(6,6)), distribution.model = "std")
Maker_Garch_4_Results <- ugarchfit(spec = Maker_Garch_4, data = Maker$Close)#;Maker_Garch_4_Results
```

## Predicting Maker 5 days out >> Using 3 days >> Dark Blue Most Optimistic, Light Blue Pessemistic
```{r}
Maker_Garch_Predict <- ugarchboot(Maker_Garch_3_Results, n.ahead = 5, method = c("Partial", "Full")[1])
plot(Maker_Garch_Predict, which = 2)
```
## Predicting Maker 5 days out >> Using 6 days >> Dark Blue Most Optimistic, Light Blue Pessemistic
```{r}
Maker_Garch_Predict_1 <- ugarchboot(Maker_Garch_4_Results, n.ahead = 5, method = c("Partial", "Full")[1])
plot(Maker_Garch_Predict_1, which = 2)
```


## Tether GARCH model building! >> We are using the Close variable this time >>
```{r}
Tether_Garch_1 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(1,1)), distribution.model = "std")
Tether_Garch_1_Results <- ugarchfit(spec = Tether_Garch_1, data = Tether$Close)

Tether_Garch_2 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(2,2)), distribution.model = "std")
Tether_Garch_2_Results <- ugarchfit(spec = Tether_Garch_2, data = Tether$Close)#;Tether_Garch_2_Results

Tether_Garch_3 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(3,3)), distribution.model = "std")
Tether_Garch_3_Results <- ugarchfit(spec = Tether_Garch_3, data = Tether$Close)#;Tether_Garch_3_Results

Tether_Garch_4 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(10,10)), distribution.model = "std")
Tether_Garch_4_Results <- ugarchfit(spec = Tether_Garch_4, data = Tether$Close)#;Tether_Garch_4_Results
```

## Predicting Tether 5 days out >> Using 3 days
```{r}
Tether_Garch_Predict <- ugarchboot(Tether_Garch_3_Results, n.ahead = 5, method = c("Partial", "Full")[1])
plot(Tether_Garch_Predict, which = 2)
```
## Predicting Tether 5 days out >> Using 6 days >> Dark Blue Most Optimistic, Light Blue Pessemistic
```{r}
Tether_Garch_Predict_1 <- ugarchboot(Tether_Garch_4_Results, n.ahead = 5, method = c("Partial", "Full")[1])
plot(Tether_Garch_Predict_1, which = 2)
```

#### Applying GARCH model to Bitcoin >> each chanhe in armaOrder is a chnage in how far back to use data
```{r}
Bitcoin_Garch_1 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(1,1)), distribution.model = "std")
Bitcoin_Garch_1_Results <- ugarchfit(spec = Bitcoin_Garch_1, data = Bitcoin$Close)

Bitcoin_Garch_2 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(2,2)), distribution.model = "std")
Bitcoin_Garch_2_Results <- ugarchfit(spec = Bitcoin_Garch_2, data = Bitcoin$Close);#Bitcoin_Garch_2_Results

Bitcoin_Garch_3 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(3,3)), distribution.model = "std")
Bitcoin_Garch_3_Results <- ugarchfit(spec = Bitcoin_Garch_3, data = Bitcoin$Close);#Bitcoin_Garch_3_Results

Bitcoin_Garch_4 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(9,9)), distribution.model = "std")
Bitcoin_Garch_4_Results <- ugarchfit(spec = Bitcoin_Garch_4, data = Bitcoin$Close);#Bitcoin_Garch_4_Results

#Bitcoin_Garch_5 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), mean.model = list(armaOrder=c(15,15)), distribution.model = "std")
#Bitcoin_Garch_5_Results <- ugarchfit(spec = Bitcoin_Garch_5, data = Bitcoin$close);Bitcoin_Garch_5_Results
```

##Predicting Using GARCH
```{r}
label_list = c("24", "25", "26", "27", "28")
Bitcoin_Garch_Predict <- ugarchboot(Bitcoin_Garch_3_Results, n.ahead = 5, method = c("Partial", "Full")[1])
#plot(Bitcoin_Garch_Predict, which = 2, xlab = label_list, xlab = "Bitcoin Volatility")  #plot.window(xlim=c(low, high), ylim=c(high,low)))
#axis(1, at=1:5, labels = label_list)
plot(Bitcoin_Garch_Predict, which = 2) #, which = 2, type ="1", xlab = "Time")
```


This Model is currenlty forcasting 5 days >> From 02/05 to 02/10 >> Dark Blue Most Optimistic, Light Blue Pessemistic >> We know that Bitcoin closed at about $8550.00 

## Another GARCH Prediction
```{r}
Bitcoin_Garch_Predict_1 <- ugarchboot(Bitcoin_Garch_4_Results, n.ahead = 5, method = c("Partial", "Full")[1])
plot(Bitcoin_Garch_Predict_1, which = 2)
```


## Getting the last day of each currency's Market Cap
```{r}
market_cap_final <- subset(crypto_ws, Date == "2018-02-23")
```

## Loading Scraped Data >> To test Model
```{r}
cyrpt_test_model <- read.csv("C:/Users/Mike/Crypto_Garch_Pred_Days.csv", skipNul = TRUE)
cyrpt_test_model$Date <- gsub("/", "" ,cyrpt_test_model$Date)
cyrpt_test_model$Date <- gsub(" ", "-", cyrpt_test_model$Date)
cyrpt_test_model$Date <- format(as.Date(cyrpt_test_model$Date, format = "%b-%d-%Y"), "%Y-%m-%d")
cyrpt_test_model <- subset(cyrpt_test_model, Date >= "2018-02-23")
## OHLC for cyrpt_test_model

i = 1
for (i in 1:nrow(cyrpt_test_model)) {
OHLC <- sum(cyrpt_test_model[i,3:6]) #;OHLC
cyrpt_test_model$OHLC[i] <- OHLC/4
}

```

## Getting some stats on our Days our GARCH model is testing
```{r}
library(dplyr)
test_stat <- cyrpt_test_model %>%
  group_by(Slug) %>%
  summarize(mean = mean(OHLC),
            std = sd(OHLC))
```

### Getting some stats for Bitcoin, Ethereum, Maker>> OHLC volatility
```{r}
bitcoin_OHLC_stat <- Bitcoin %>%
  summarise(mean = mean(OHLC),
            std = sd(OHLC))
ethereum_OHLC_stat <- Ethereum %>%
  summarise(mean = mean(OHLC),
            std = sd(OHLC))
maker_OHLC_stat <- Maker %>%
  summarise(mean = mean(OHLC),
            std = sd(OHLC))
Tether %>%
  summarise(mean = mean(OHLC),
            std = sd(OHLC))
```

